\documentclass{cv}

%To set the page margins
\geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\begin{document}

%About me
\name{Anuj Nagpal}
\aftername{2nd Year Undergraduate}
\aftername{Department of Computer Science and Engineering}
\aftername{Indian Institute of Technology, Kanpur}
\aftername{Address: Room No. 366, Hall 3, IIT Kanpur}
\aftername{Email: anujnag@cse.iitk.ac.in, anujnagpal96@gmail.com}
\aftername{Phone: +91-7755047730}

%For remaining sections and subsections, heading will make it clear what they contain

\section*{Educational Qualifications:}
\begin{center}
\begin{tabular}{ | m{2.4cm} | m{6.5cm} | m{5.7cm} | m{1.2cm}| } 
 \hline
 \begin{center} \textbf{Year} \end{center} 
 & \begin{center} \textbf{Degree} \end{center} 
 & \begin{center} \textbf{Institute} \end{center} 
 & \begin{center} \textbf{CPI/\%} \end{center} \\ 
 \hline
 \begin{center} 2018(expected) \end{center}
  & \begin{center} Bachelor of Technology, Computer Science and Engineering \end{center}
  & \begin{center} Indian Institute of Technology Kanpur \end{center} 
  & 9.5/10.0 \\
 \hline 
 \begin{center} 2014 \end{center} 
 & \begin{center} All India Senior School Certificate Examination (Class XII - CBSE) \end{center} 
 & \begin{center} Bal Mandir Model Sen. Sec. School, Mandi Killianwali \end{center} 
 & \begin{center} 96.2\% \end{center} \\
 \hline
 \begin{center} 2012 \end{center} 
 & \begin{center} All India Secondary School Examination (Class X - CBSE) \end{center} 
 & \begin{center} Bal Mandir Model Sen. Sec. School Mandi Killianwali \end{center} 
 & \begin{center} 10/10 \end{center} \\
 \hline
\end{tabular}
\end{center}

\section*{Academic Achievements}
\begin{itemize}
\item Secured an All India Rank of 190 in JEE Advanced 2014 given by about 150,000 students.
\item Secured an All India Rank of 220 and State Rank of 4 in Punjab in JEE Main 2014 given by about 1,500,000
students.
\item Qualified National Standard Examination in Chemistry (NSEC) and National Standard Examination in Astronomy (NSEA)
in 2013.
\item Conferred with Kishore Vaigyanik Protsahan Yojana (KVPY) Scholarship in 2012 conducted by IISc Bangalore.
\end{itemize}

\section*{Projects}
\datedsubsection{Joint Seat Allocation for IITs, NITs, IIITs and GFTIs 2016}{Dec '15 - Current}
(under Dr. Surendra Baswana)
\begin{itemize}
\item Designing a DA algorithm as per the business rules of JoSAA 2016 for the Joint Seat Allocation 2016.
\item Coding an implementation of the algorithm and testing it on synthetic data as test cases.
\item Designed the validation modules that were used to confirm that all the business rules were being followed correctly.
\end{itemize}

\datedsubsection{Combinatorial Game Theory}{Jul '15 – Nov ‘15}
(course project under Dr. Rajat Mittal )
\begin{itemize}
\item Studied game trees, impartial games, sums, comparisons, outcome classes in combinatorial games.
\item Analysis and study of proofs of results related to some combinatorial games like Nim, Hex, Domineering and
Tic Tac Toe.
\item Studied Minimax and Monte Carlo Algorthm for Tic Tac Toe.
\end{itemize}

\datedsubsection{Learn With Fun App}{Sep '15}
\begin{itemize}
\item Built an App in Microsoft.Code.Fun.Do Hackathon to help school students to gain basic programming knowledge
as if they are reading a story book.
\item Coded it in C\# using Visual Studio 2015 and used Adobe Photoshop to design the pages.
\end{itemize}

\datedsubsection{Vegetable Shredder and Chopper}{Jul '15 - Nov '15}
( under Dr. Anish Upadhyaya )
\begin{itemize}
\item Ranked 2 in day-wise section teams for designing and creating a mechanical vegetable shredder and chopper
under the Manufacturing Processes course.
\item Worked on it along with 4 other students using the processes taught in the course.
\end{itemize}

\subsection*{Positions of Responsibility:}
\begin{itemize}
\item Secretary, Programming Club
\begin{flushright}
Apr '15 - Current
\end{flushright}
\item Secretary, Animation Club
\begin{flushright}
Apr '15 - Current
\end{flushright}
\item UG Secretary, Association of Computing Activities, Student Body of CSE Department, IIT Kanpur
\begin{flushright}
Apr '15 - Current
\end{flushright}
\item Senior Web Executive, Techkriti 2016
\end{itemize}

\section*{Relevant Courses}
\begin{multicols}{2}	
\begin{itemize}
\item ESC101 - Fundamentals of Computing
\item CS210 - Data Structures and Algorithms*
\item CS251 - Computing Laboratory*
\item CS201 - Discrete Mathematics
\item CS202 - Introduction to Logic
\item CS203 - Abstract Algebra
\item CS220 - Computer Organization*
\item MSO201 - Probability and Statistics*
\item MTH102 - Linear Algebra and ODE
\item MTH101 - Analytical Calculus
\item ESC201 – Introduction to Electronics
\end{itemize}
\end{multicols}
\begin{flushright}
* \ - \ Ongoing
\end{flushright}

\section*{Technical Skills}
\begin{itemize}
\item \textbf{\underline{Programming Languages:}} \\ \\
C, C++, Python, Java, C\#, Bash, Perl, HTML5, CSS , JavaScript, PHP, MySQL, Verilog, Assembly
\item \textbf{\underline{Softwares \& Utilities:}} \\ \\
MATLAB, GNU Octave, Git, Latex, Adobe Photoshop, Autodesk 3ds Max
\end{itemize}
\end{document} 